Who Needs Privacy? Exploring the relationship between personality and need for privacy

### 2023-03-01 analyses.RmD
- added results to CFAs

- At this point, we haven't yet collected data. 
- The results below use simulated data. 
- The data are random and don't make sense, but help to illustrate the overall approach and planned analyses.
- We'll later conduct additional analyses, for example model-alterations given misfit.

@@

```{r r-setup, include=T, echo=F}
# install packages
# devtools::install_github("https://github.com/tdienlin/td")

@@

```{r}
model <- "HEX_HOH_SIN =~ HEX_HOH_SIN_01 + HEX_HOH_SIN_02 + HEX_HOH_SIN_03 + HEX_HOH_SIN_04"
```

@@

```{r}
model <- "HEX_HOH_FAI =~ HEX_HOH_FAI_01 + HEX_HOH_FAI_02 + HEX_HOH_FAI_03 + HEX_HOH_FAI_04"
```

@@

```{r}
model <- "HEX_HOH_GRE =~ HEX_HOH_GRE_01 + HEX_HOH_GRE_02 + HEX_HOH_GRE_03 + HEX_HOH_GRE_04"
```

@@

```{r}
model <- "HEX_HOH_MOD =~ HEX_HOH_MOD_01 + HEX_HOH_MOD_02 + HEX_HOH_MOD_03 + HEX_HOH_MOD_04"
```

@@

```{r}
model <- "HEX_EMO_FEA =~ HEX_EMO_FEA_01 + HEX_EMO_FEA_02 + HEX_EMO_FEA_03 + HEX_EMO_FEA_04"
```

@@

```{r}
model <- "HEX_EMO_ANX =~ HEX_EMO_ANX_01 + HEX_EMO_ANX_02 + HEX_EMO_ANX_03 + HEX_EMO_ANX_04"
```

@@

```{r}
model <- "HEX_EMO_DEP =~ HEX_EMO_DEP_01 + HEX_EMO_DEP_02 + HEX_EMO_DEP_03 + HEX_EMO_DEP_04"
```

@@

```{r}
model <- "HEX_EMO_SEN =~ HEX_EMO_SEN_01 + HEX_EMO_SEN_02 + HEX_EMO_SEN_03 + HEX_EMO_SEN_04"
```

@@

```{r}
model <- "HEX_EXT_SSE =~ HEX_EXT_SSE_01 + HEX_EXT_SSE_02 + HEX_EXT_SSE_03 + HEX_EXT_SSE_04"
```

@@

```{r}
model <- "HEX_EXT_BOL =~ HEX_EXT_BOL_01 + HEX_EXT_BOL_02 + HEX_EXT_BOL_03 + HEX_EXT_BOL_04"
```

@@

```{r}
model <- "HEX_EXT_SOC =~ HEX_EXT_SOC_01 + HEX_EXT_SOC_02 + HEX_EXT_SOC_03 + HEX_EXT_SOC_04"
```

@@

```{r}
model <- "HEX_EXT_LIV =~ HEX_EXT_LIV_01 + HEX_EXT_LIV_02 + HEX_EXT_LIV_03 + HEX_EXT_LIV_04"
```

@@

```{r}
model <- "HEX_AGR_FOR =~ HEX_AGR_FOR_01 + HEX_AGR_FOR_02 + HEX_AGR_FOR_03 + HEX_AGR_FOR_04"
```

@@

```{r}
model <- "HEX_AGR_GEN =~ HEX_AGR_GEN_01 + HEX_AGR_GEN_02 + HEX_AGR_GEN_03 + HEX_AGR_GEN_04"
```

@@

```{r}
model <- "HEX_AGR_FLX =~ HEX_AGR_FLX_01 + HEX_AGR_FLX_02 + HEX_AGR_FLX_03 + HEX_AGR_FLX_04"
```

@@

```{r}
model <- "HEX_AGR_PAT =~ HEX_AGR_PAT_01 + HEX_AGR_PAT_02 + HEX_AGR_PAT_03 + HEX_AGR_PAT_04"
```

@@

```{r}
model <- "HEX_CNS_ORG =~ HEX_CNS_ORG_01 + HEX_CNS_ORG_02 + HEX_CNS_ORG_03 + HEX_CNS_ORG_04"
```

@@

```{r}
model <- "HEX_CNS_DIL =~ HEX_CNS_DIL_01 + HEX_CNS_DIL_02 + HEX_CNS_DIL_03 + HEX_CNS_DIL_04"
```

@@

```{r}
model <- "HEX_CNS_PER =~ HEX_CNS_PER_01 + HEX_CNS_PER_02 + HEX_CNS_PER_03 + HEX_CNS_PER_04"
```

@@

```{r}
model <- "HEX_CNS_PRU =~ HEX_CNS_PRU_01 + HEX_CNS_PRU_02 + HEX_CNS_PRU_03 + HEX_CNS_PRU_04"
```

@@

```{r}
model <- "HEX_OPN_AES =~ HEX_OPN_AES_01 + HEX_OPN_AES_02 + HEX_OPN_AES_03 + HEX_OPN_AES_04"
```

@@

```{r}
model <- "HEX_OPN_INQ =~ HEX_OPN_INQ_01 + HEX_OPN_INQ_02 + HEX_OPN_INQ_03 + HEX_OPN_INQ_04"
```

@@

```{r}
model <- "HEX_OPN_CRE =~ HEX_OPN_CRE_01 + HEX_OPN_CRE_02 + HEX_OPN_CRE_03 + HEX_OPN_CRE_04"
```

@@

```{r}
model <- "HEX_OPN_UNC =~ HEX_OPN_UNC_01 + HEX_OPN_UNC_02 + HEX_OPN_UNC_03 + HEX_OPN_UNC_04"
```

@@

```{r}
model <- "HEX_ALT =~ HEX_ALT_01 + HEX_ALT_02 + HEX_ALT_03 + HEX_ALT_04"
```

@@

```{r}
model <- "NFP_PSY =~ NFP_PSY_01 + NFP_PSY_02 + NFP_PSY_03 + NFP_PSY_04"
```

@@

```{r}
model <- "NFP_PHY =~ NFP_PHY_01 + NFP_PHY_02 + NFP_PHY_03 + NFP_PHY_04"
```

@@

```{r}
model <- "NFP_SOC =~ NFP_SOC_01 + NFP_SOC_02 + NFP_SOC_03 + NFP_SOC_04"
```

@@

```{r}
model <- "NFP_GOV =~ NFP_GOV_01 + NFP_GOV_02 + NFP_GOV_03 + NFP_GOV_04"
```

@@

```{r}
model <- "NFP_COM =~ NFP_COM_01 + NFP_COM_02 + NFP_COM_03 + NFP_COM_04"
```

@@

```{r}
model <- "NFP_INF =~ NFP_INF_01 + NFP_INF_02 + NFP_INF_03 + NFP_INF_04"
```

@@

```{r}
model <- "NFP_ANO =~ NFP_ANO_01 + NFP_ANO_02 + NFP_ANO_03 + NFP_ANO_04"
```

@@

```{r}
model <- "NFP_GEN =~ NFP_GEN_01 + NFP_GEN_02 + NFP_GEN_03 + NFP_GEN_04"
```

@@

A 5% error rate would imply collecting 1.293 participants.

>>>>

- At this point, we haven't yet collected data. 
- The results below use simulated data. 
- The data are random and don't make sense, but help to illustrate the overall approach and planned analyses.
- We'll later conduct further analyses not yet reported here, for example model-alterations given misfit.

@@

```{r r-setup, include=T, echo=T, results='hide'}
# install packages
# devtools::install_github("https://github.com/tdienlin/td")

@@

```{r}
name <- "HEX_HOH_SIN"
model <- "HEX_HOH_SIN =~ HEX_HOH_SIN_01 + HEX_HOH_SIN_02 + HEX_HOH_SIN_03 + HEX_HOH_SIN_04"
assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
```

@@

```{r}
name <- "HEX_HOH_FAI"
model <- "HEX_HOH_FAI =~ HEX_HOH_FAI_01 + HEX_HOH_FAI_02 + HEX_HOH_FAI_03 + HEX_HOH_FAI_04"
assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
```

@@

```{r}
name <- "HEY_HOH_GRE"
model <- "HEX_HOH_GRE =~ HEX_HOH_GRE_01 + HEX_HOH_GRE_02 + HEX_HOH_GRE_03 + HEX_HOH_GRE_04"
assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
```

@@

```{r}
name <- "HEX_HOH_MOD"
model <- "HEX_HOH_MOD =~ HEX_HOH_MOD_01 + HEX_HOH_MOD_02 + HEX_HOH_MOD_03 + HEX_HOH_MOD_04"
assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
```

@@

```{r}
name <- "HEX_EMO_FEA"
model <- "HEX_EMO_FEA =~ HEX_EMO_FEA_01 + HEX_EMO_FEA_02 + HEX_EMO_FEA_03 + HEX_EMO_FEA_04"
assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
```

@@

```{r}
name <- "HEX_EMO_ANX"
model <- "HEX_EMO_ANX =~ HEX_EMO_ANX_01 + HEX_EMO_ANX_02 + HEX_EMO_ANX_03 + HEX_EMO_ANX_04"
assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
```

@@

```{r}
name <- "HEX_EMO_DEP"
model <- "HEX_EMO_DEP =~ HEX_EMO_DEP_01 + HEX_EMO_DEP_02 + HEX_EMO_DEP_03 + HEX_EMO_DEP_04"
assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
```

@@

```{r}
name <- "HEX_EMO_SEN"
model <- "HEX_EMO_SEN =~ HEX_EMO_SEN_01 + HEX_EMO_SEN_02 + HEX_EMO_SEN_03 + HEX_EMO_SEN_04"
assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
```

@@

```{r}
name <- "HEX_EXT_SSE"
model <- "HEX_EXT_SSE =~ HEX_EXT_SSE_01 + HEX_EXT_SSE_02 + HEX_EXT_SSE_03 + HEX_EXT_SSE_04"
assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
```

@@

```{r}
name <- "HEX_EXT_BOL"
model <- "HEX_EXT_BOL =~ HEX_EXT_BOL_01 + HEX_EXT_BOL_02 + HEX_EXT_BOL_03 + HEX_EXT_BOL_04"
assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
```

@@

```{r}
name <- "HEX_EXT_SOC"
model <- "HEX_EXT_SOC =~ HEX_EXT_SOC_01 + HEX_EXT_SOC_02 + HEX_EXT_SOC_03 + HEX_EXT_SOC_04"
assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
```

@@

```{r}
name <- "HEX_EXT_LIV"
model <- "HEX_EXT_LIV =~ HEX_EXT_LIV_01 + HEX_EXT_LIV_02 + HEX_EXT_LIV_03 + HEX_EXT_LIV_04"
assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
```

@@

```{r}
name <- "HEX_AGR_FOR"
model <- "HEX_AGR_FOR =~ HEX_AGR_FOR_01 + HEX_AGR_FOR_02 + HEX_AGR_FOR_03 + HEX_AGR_FOR_04"
assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
```

@@

```{r}
name <- "HEX_AGR_GEN"
model <- "HEX_AGR_GEN =~ HEX_AGR_GEN_01 + HEX_AGR_GEN_02 + HEX_AGR_GEN_03 + HEX_AGR_GEN_04"
assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
```

@@

```{r}
name <- "HEX_AGR_FLX"
model <- "HEX_AGR_FLX =~ HEX_AGR_FLX_01 + HEX_AGR_FLX_02 + HEX_AGR_FLX_03 + HEX_AGR_FLX_04"
assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
```

@@

```{r}
name <- "HEX_AGR_PAT"
model <- "HEX_AGR_PAT =~ HEX_AGR_PAT_01 + HEX_AGR_PAT_02 + HEX_AGR_PAT_03 + HEX_AGR_PAT_04"
assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
```

@@

```{r}
name <- "HEX_CNS_ORG"
model <- "HEX_CNS_ORG =~ HEX_CNS_ORG_01 + HEX_CNS_ORG_02 + HEX_CNS_ORG_03 + HEX_CNS_ORG_04"
assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
```

@@

```{r}
name <- "HEX_CNS_DIL"
model <- "HEX_CNS_DIL =~ HEX_CNS_DIL_01 + HEX_CNS_DIL_02 + HEX_CNS_DIL_03 + HEX_CNS_DIL_04"
assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
```

@@

```{r}
name <- "HEX_CNS_PER"
model <- "HEX_CNS_PER =~ HEX_CNS_PER_01 + HEX_CNS_PER_02 + HEX_CNS_PER_03 + HEX_CNS_PER_04"
assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
```

@@

```{r}
name <- "HEX_CNS_PRU"
model <- "HEX_CNS_PRU =~ HEX_CNS_PRU_01 + HEX_CNS_PRU_02 + HEX_CNS_PRU_03 + HEX_CNS_PRU_04"
assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
```

@@

```{r}
name <- "HEX_OPN_AEX"
model <- "HEX_OPN_AES =~ HEX_OPN_AES_01 + HEX_OPN_AES_02 + HEX_OPN_AES_03 + HEX_OPN_AES_04"
assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
```

@@

```{r}
name <- "HEX_OPN_INQ"
model <- "HEX_OPN_INQ =~ HEX_OPN_INQ_01 + HEX_OPN_INQ_02 + HEX_OPN_INQ_03 + HEX_OPN_INQ_04"
assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
```

@@

```{r}
name <- "HEX_OPN_CRE"
model <- "HEX_OPN_CRE =~ HEX_OPN_CRE_01 + HEX_OPN_CRE_02 + HEX_OPN_CRE_03 + HEX_OPN_CRE_04"
assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
```

@@

```{r}
name <- "HEX_OPN_UNC"
model <- "HEX_OPN_UNC =~ HEX_OPN_UNC_01 + HEX_OPN_UNC_02 + HEX_OPN_UNC_03 + HEX_OPN_UNC_04"
assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
```

@@

```{r}
name <- "HEX_ALT"
model <- "HEX_ALT =~ HEX_ALT_01 + HEX_ALT_02 + HEX_ALT_03 + HEX_ALT_04"
assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
```

@@

```{r}
name <- "NFP_PSY"
model <- "NFP_PSY =~ NFP_PSY_01 + NFP_PSY_02 + NFP_PSY_03 + NFP_PSY_04"
assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
```

@@

```{r}
name <- "NFP_PHY"
model <- "NFP_PHY =~ NFP_PHY_01 + NFP_PHY_02 + NFP_PHY_03 + NFP_PHY_04"
assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
```

@@

```{r}
name <- "NFP_SOC"
model <- "NFP_SOC =~ NFP_SOC_01 + NFP_SOC_02 + NFP_SOC_03 + NFP_SOC_04"
assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
```

@@

```{r}
name <- "NFP_GOV"
model <- "NFP_GOV =~ NFP_GOV_01 + NFP_GOV_02 + NFP_GOV_03 + NFP_GOV_04"
assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
```

@@

```{r}
name <- "NFP_COM"
model <- "NFP_COM =~ NFP_COM_01 + NFP_COM_02 + NFP_COM_03 + NFP_COM_04"
assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
```

@@

```{r}
name <- "NFP_INF"
model <- "NFP_INF =~ NFP_INF_01 + NFP_INF_02 + NFP_INF_03 + NFP_INF_04"
assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
```

@@

```{r}
name <- "NFP_ANO"
model <- "NFP_ANO =~ NFP_ANO_01 + NFP_ANO_02 + NFP_ANO_03 + NFP_ANO_04"
assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
```

@@

```{r}
name <- "NFP_GEN"
model <- "NFP_GEN =~ NFP_GEN_01 + NFP_GEN_02 + NFP_GEN_03 + NFP_GEN_04"
assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
```

@@

A 5% error rate would imply collecting `r power_n_95` participants.
